---
title: "Chinese economy network analysis"
output:
  word_document:
    toc: yes
  pdf_document:
    extra_dependencies:
      ctexcap: UTF8
    latex_engine: xelatex
    toc: yes
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, cache=T)
pacman::p_load(ggplot2, data.table, stringr, dplyr, tidyr, 
               glmnet, xtable, doParallel, scales, plm, lfe, lme4, igraph)

# source("../../AllData/AIS/R/heatmap.R")

if(.Platform$OS.type=="windows") {
  setwd("C:/Users/junhui/Dropbox (Penn)/Linda_Wu Zhu/Data & Codes")
  Sys.setlocale(category = "LC_CTYPE", locale = "chs")
}

source("src/utilities.R")
```

```{r read long panel, cache.lazy=FALSE}
years <- seq(2002, 2017)
nets <- paste("net", years, sep="")
pan <- list()
for (i in years) {
  v <- fread(paste("dynamic_networks/holding_networks_", i, "_WT.csv", sep=""),
             header = T, encoding = "UTF-8", stringsAsFactors = F)
  v$year <- i
  pan[[i]] <- v
}
pan <- rbindlist(pan)
```

# EDA
## Number of investors and investees
```{r}
num_investor_investee <- data.table(year         = years, 
                                    num_investor = pan[,length(unique(new_entid_investor)), by=year][,V1],
                                    num_investee = pan[,length(unique(new_entid_invested)), by=year][,V1])

num_investor_investee %>% melt(id.vars = "year") %>%
  ggplot() + geom_bar(aes(x=year, y=value, fill=variable), stat="identity", position="dodge") +
    ggtitle("Number of investors and investees across years") + 
    theme(axis.text.x = element_text(angle = 30, hjust = 1)) + 
  xlab("Year") + ylab("Number of investors/investees") 
```

```{r xtable num investor investee, echo=F, message=F, results='asis'}
print(xtable(num_investor_investee), include.rownames=F)
```
## Sum of investment across year
```{r invest cash across year}
pan[, sum(cash, na.rm=T), by=year] %>% rename(investment = V1) %>%
  ggplot() + geom_bar(aes(x=year, y=investment, fill=investment), stat="identity") +
    ggtitle("Sum of investment") + 
    theme(axis.text.x = element_text(angle = 30, hjust = 1)) + 
  xlab("Year") + ylab("Investment") + 
  scale_fill_distiller(type="seq", palette="YlGnBu", direction=1)

```

```{r xtable sum inv, echo=F, message=F, results='asis'}
print(xtable(pan[, sum(cash, na.rm=T), by=year] %>% rename(investment = V1)), include.rownames=F)
```

## Number of firms established across year

## Number of entrants and exits of the network
```{r in-out}
entrants_exiting_table <- data.table(year     = seq(2003, 2017), 
                                     entrants = rep(0, 15), 
                                     exit     = rep(0, 15))
for(i in seq(2003, 2017)) {
  print(i)
  firm_pre_year <- unique(c(pan[year==(i-1), new_entid_invested], pan[year==(i-1), new_entid_investor]))
  firm_cur_year <- unique(c(pan[year==(i), new_entid_invested], pan[year==(i), new_entid_investor]))
  entrants_exiting_table[year==i, exit:=as.integer(sum(!(firm_pre_year %in% firm_cur_year)))]
  entrants_exiting_table[year==i, entrants:=as.integer(sum(!(firm_cur_year %in% firm_pre_year)))]
}

entrants_exiting_table %>% melt(id.vars = "year") %>%
  ggplot() + geom_bar(aes(x=year, y=value, fill=variable), stat="identity", position="dodge") +
    ggtitle("Number of entrants and exits across years") + 
    theme(axis.text.x = element_text(angle = 30, hjust = 1)) + 
  xlab("Year") + ylab("Number of entrants/exits") 
```

```{r xtable in out, echo=F, message=F, results='asis'}
print(xtable(entrants_exiting_table), include.rownames=F)
```

## Firms with sum invest amount change (registered capital changed?)
```{r reg cap changed}
tmp = pan[, sum(cash, na.rm=T), by=c("year", "new_entid_invested")]
changed_regcap <- tmp[, length(unique(V1))!=1, by=new_entid_invested]
entid_changed_regcap <- changed_regcap[V1==TRUE, new_entid_invested]
entid_changed_year <- tmp[new_entid_invested %in% entid_changed_regcap,
                          year[1+which(diff(V1)!=0)], by=new_entid_invested]
View(tmp[new_entid_invested %in% entid_changed_regcap])

plot_discrete_range(entid_changed_year$V1, name="Number of firms changed regcap")
```
There are in total `r length(entid_changed_regcap)` of firms changed registered capital.


```{r update info, cache=F}
update_info <- fread("update_info/update_info_v2.csv", encoding = "UTF-8")
update_info <- update_info[, year:=substr(dateid, 0, 4)]
tmp = update_info[, .(sum_before = sum(beforecash, na.rm=T),
                      sum_after = sum(aftercash, na.rm=T)), 
                  by=c("year", "entid_invested")]
changed_regcap <- tmp[sum_before!=sum_after][order(year)]
plot_discrete_range(changed_regcap$year, range = c(1982, 2017), name="Number of firms changed regcap")
```

## Match AIS
### Summary statistics of ROA across year

# cnpc
```{r cnpc}
cnpc <- pan[new_entid_investor=="551997"]

cnpc[, .N, by=year] %>% rename(num_inv = N) %>% 
ggplot() + geom_bar(aes(x=year, y=num_inv, fill=num_inv), stat="identity") +
    ggtitle("Num of investment") + 
    theme(axis.text.x = element_text(angle = 30, hjust = 1)) + 
  xlab("Year") + ylab("Investment") + 
  scale_fill_distiller(type="seq", palette="YlGnBu", direction=1)
```

```{r cnpc sum}
cnpc[, sum(cash, na.rm=T), year] %>% rename(sum_inv = V1) %>%
ggplot() + geom_bar(aes(x=year, y=sum_inv, fill=sum_inv), stat="identity") +
    ggtitle("Sum of investment") + 
    theme(axis.text.x = element_text(angle = 30, hjust = 1)) + 
  xlab("Year") + ylab("Investment") + 
  scale_fill_distiller(type="seq", palette="YlGnBu", direction=1)
```


```{r xtable cnpc, echo=F, message=F, results='asis'}
print(xtable(cnpc[new_entid_invested=="552219", .(new_entid_invested, new_entid_investor, cash, share, year)]), include.rownames=F)
```


# Haier
```{r haier, eval=F}
num_inv_haier <- pan[new_entid_investor=="5792800", .N, by=year]
sum_inv_haier <- pan[new_entid_investor=="5792800", sum(cash, na.rm=T), by=year]

```

# Huawei
```{r huawei, eval=F}
View(pan[new_entid_invested=="1290817"])
# Who is huawei's investor? 1290822
View(pan[new_entid_investor=="1290817"])

```

# Investment changes
```{r inv change tab}
inv_change_table <- pan[,sum(length(unique(cash))>1), by=c("new_entid_invested", "new_entid_investor")][V1!=0]
inv_change_firm <- unique(c(inv_change_table$new_entid_invested, inv_change_table$new_entid_investor))
# View(basic_info[new_entid%in%inv_change_firm])
```

There are in total `r nrow(unique(inv_change_table[,.(new_entid_invested, new_entid_investor)]))` (`r percent(nrow(unique(inv_change_table[,.(new_entid_invested, new_entid_investor)]))/nrow(unique(pan[,.(new_entid_invested, new_entid_investor)])))`) pairs of investors and investees changed the amount of investment across the years.

```{r investee change}
reg_cap_change_investee <- pan[,sum(length(unique(reg_cap_invested))>1), by=new_entid_invested][V1!=0]
View(pan[new_entid_invested %in% reg_cap_change_investee$new_entid_invested])

```

# Compare regiatered capital vs AIS paidin capital
```{r read ais and matching, cache=F}
ais <- fread("C:/Users/junhui/Dropbox (Penn)/AllData/AIS/data/processed_data/panel_name_61.csv", encoding = "UTF-8")
ais_matching <- fread("AIS_CRCS_Matching/ASCIE_CRCS_matching.csv", encoding = "UTF-8", fill=T)
```

```{r match ais paid in vs reg cap}
source("C:/Users/junhui/Dropbox (Penn)/AllData/AIS/R/preprocess_ownership.R")
ais <- preprocess.cap(ais)
ais_vs_net <- merge(ais[id!="",.(id, paidincap, year)], 
                    ais_matching[firm_code!=""], 
                    by.x=c("id", "year"), by.y=c("firm_code", "year"))
ais_vs_net <- merge(ais_vs_net, 
                    pan[new_entid_invested!="",.(new_entid_invested, reg_cap_invested, year)],
                    by.x=c("new_entid", "year"), by.y=c("new_entid_invested", "year"))
ais_vs_net <- unique(ais_vs_net, by=c("new_entid", "year"))

# scale paidin cap into 10k
ais_vs_net <- ais_vs_net[,paidincap:=paidincap/10]
```

We look into the difference between the paidin capital and registered capital.

We keep those companies with non zero paidin and nonzeor registered capital and thus droppoing `r ais_vs_net[!(paidincap!=0 & reg_cap_invested!=0),.N]/ais_vs_net[,.N]` observations in total acrosss years.

```{r sum paidin vs reg cap}
paidin_vs_regcap_by_year <- ais_vs_net[paidincap!=0 & reg_cap_invested!=0,
                                       .(paidincap_sum = sum(paidincap,na.rm = T),
                                          regcap_sum = sum(reg_cap_invested, na.rm = T)), year]

paidin_vs_regcap_by_year %>% melt(id.vars = "year") %>%
  ggplot() + geom_bar(aes(x=year, y=value, fill=variable), stat="identity", position="dodge") +
    ggtitle("Sum of Paidin capital vs Registered capital of investees AIS firms") + 
    theme(axis.text.x = element_text(angle = 30, hjust = 1)) + 
  xlab("Year") + ylab("10k RMB")
```

```{r padin vs regcap ais investee table, echo=F, message=FALSE, warning=FALSE, results='asis'}
print(xtable(paidin_vs_regcap_by_year), include.rownames=F)
```

```{r mean paidin vs reg cap}
paidin_vs_regcap_mean_by_year <- ais_vs_net[paidincap!=0 & reg_cap_invested!=0,
                                            .(paidincap_sum = mean(paidincap,na.rm = T),
                                              regcap_sum = mean(reg_cap_invested, na.rm = T)), year]

paidin_vs_regcap_mean_by_year %>% melt(id.vars = "year") %>%
  ggplot() + geom_bar(aes(x=year, y=value, fill=variable), stat="identity", position="dodge") +
    ggtitle("Mean of Paidin capital vs Registered capital of investees AIS firms") + 
    theme(axis.text.x = element_text(angle = 30, hjust = 1)) + 
  xlab("Year") + ylab("10k RMB")
```

```{r mean padin vs regcap ais investee table, echo=F, message=FALSE, warning=FALSE, results='asis'}
print(xtable(paidin_vs_regcap_mean_by_year[order(paidin_vs_regcap_mean_by_year[,year])]), include.rownames=F)
```

```{r hist 2002}
hist(ais_vs_net[year==2002 & paidincap!=0 & reg_cap_invested!=0, reg_cap_invested-paidincap],breaks=100)
hist(ais_vs_net[year==2002 & paidincap!=0 & reg_cap_invested!=0 &
                  reg_cap_invested-paidincap < 1e3 & reg_cap_invested-paidincap > -1e3, reg_cap_invested-paidincap], breaks=100)
ais_vs_net[year==2002 & paidincap!=0 & reg_cap_invested!=0 &
                  reg_cap_invested-paidincap < 100 & reg_cap_invested-paidincap > -100, .N]/ais_vs_net[year==2002,.N]

ais_vs_net[paidincap!=0 & reg_cap_invested!=0, diff_rate:=(reg_cap_invested-paidincap)/reg_cap_invested]
summary(ais_vs_net[paidincap!=0 & reg_cap_invested!=0,diff_rate])

ais_vs_net[paidincap!=0 & reg_cap_invested!=0, mean(diff_rate, na.rm=T), year] %>%
  rename("diff_rate"=V1) %>%
ggplot() + geom_bar(aes(x=year, y=diff_rate, fill=diff_rate), stat="identity") +
    ggtitle("Mean of (Reg_cap - Paidin)/Reg_cap") + 
    theme(axis.text.x = element_text(angle = 30, hjust = 1)) + 
  xlab("Year") + ylab("Investment") + 
  scale_fill_distiller(type="seq", palette="YlGnBu")
```
## Serveral firms


### SOE: ZTE 27939873X

```{r an gang, echo=F, message=FALSE, warning=FALSE, results='asis'}
gm <- ais_vs_net[id=="27939873X",.(new_entid, paidincap, reg_cap_invested, year)]
setkey(gm, year)
gm_num_investor <- pan[new_entid_invested=="521576",
    length(unique(new_entid_investor)),by=year]
gm <- merge(gm, gm_num_investor, by="year")
setnames(gm, "V1", "num_investor")
print(xtable(gm), include.rownames=F)
```

### Collective: Huawei (or private) 192203821
```{r huawei 2, echo=F, message=FALSE, warning=FALSE, results='asis'}
gm <- ais_vs_net[id=="192203821",.(new_entid, paidincap, reg_cap_invested, year)]
setkey(gm, year)
gm_num_investor <- pan[new_entid_invested=="1290817",
    length(unique(new_entid_investor)),by=year]
gm <- merge(gm, gm_num_investor, by="year")
setnames(gm, "V1", "num_investor")
print(xtable(gm), include.rownames=F)
```


### HTM: Guangzhou P&G 618404218

```{r png, echo=F, message=FALSE, warning=FALSE, results='asis'}
gm <- ais_vs_net[id=="618404218",.(new_entid, paidincap, reg_cap_invested, year)]
setkey(gm, year)
gm_num_investor <- pan[new_entid_invested=="2612006",
    length(unique(new_entid_investor)),by=year]
gm <- merge(gm, gm_num_investor, by="year")
setnames(gm, "V1", "num_investor")
print(xtable(gm), include.rownames=F)
```


### Private:　Media  722473344

```{r media, echo=F, message=FALSE, warning=FALSE, results='asis'}
gm <- ais_vs_net[id=="722473344",.(new_entid, paidincap, reg_cap_invested, year)]
setkey(gm, year)
gm_num_investor <- pan[new_entid_invested=="4979839",
    length(unique(new_entid_investor)),by=year]
gm <- merge(gm, gm_num_investor, by="year")
setnames(gm, "V1", "num_investor")
print(xtable(gm), include.rownames=F)
```


### Private: Wanxiang 142911934
```{r wanxiang, echo=F, message=FALSE, warning=FALSE, results='asis'}
gm <- ais_vs_net[id=="142911934",.(new_entid, paidincap, reg_cap_invested, year)]
setkey(gm, year)
gm_num_investor <- pan[new_entid_invested=="47142",
    length(unique(new_entid_investor)),by=year]
gm <- merge(gm, gm_num_investor, by="year")
setnames(gm, "V1", "num_investor")
print(xtable(gm), include.rownames=F)
```

### Foreign: Samsung 617882066

```{r Samsung, echo=F, message=FALSE, warning=FALSE, results='asis'}
gm <- ais_vs_net[id=="617882066",.(new_entid, paidincap, reg_cap_invested, year)]
setkey(gm, year)
gm_num_investor <- pan[new_entid_invested=="2847008",
    length(unique(new_entid_investor)),by=year]
gm <- merge(gm, gm_num_investor, by="year")
setnames(gm, "V1", "num_investor")
print(xtable(gm), include.rownames=F)
```

### Joint venture: Shanghai GM

```{r shanghai gm, echo=F, message=FALSE, warning=FALSE, results='asis'}
gm <- ais_vs_net[id=="607371748",.(new_entid, paidincap, reg_cap_invested, year)]
setkey(gm, year)
gm_num_investor <- pan[new_entid_invested=="72398" | new_entid_invested=="607371748",
    length(unique(new_entid_investor)),by=year]
gm <- merge(gm, gm_num_investor, by="year")
setnames(gm, "V1", "num_investor")
print(xtable(gm), include.rownames=F)
```

